Sound Automated Synthesis of Digital Controllers

### 2016-10-13 paper/paper.tex
fix typos

The digital controllers synthesized in this paper are typically used in closed loops with continuous (and physical) plants. Thus, the proposed approach have to consider dynamics of continuous parts of system ({\it e.g.}, plant) and discrete parts ({\it e.g.}, digital controller), {\it i.e.} the synthesized controller have to consider the issues related to the hybrid systems studies.

@@

%------------------------------------
%\subsection{Using Fixed Point Arithmetic for verification}
%\label{fixedpoint_verification}
%------------------------------------
>>>>>>> 37d4cc3c530b25bf97f1052f7c187af06f832aea

>>>>

The digital controllers synthesized in this paper are typically used in closed loops with continuous (and physical) plants. Thus, the proposed approach has to consider dynamics of continuous parts of system ({\it e.g.}, plant) and discrete parts ({\it e.g.}, digital controller), {\it i.e.} the synthesized controller has to consider the issues related to the hybrid systems studies.

@@

%------------------------------------
%\subsection{Using Fixed Point Arithmetic for verification}
%\label{fixedpoint_verification}
%------------------------------------
